Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-20 p2/axiom-def.tex
Final changes

% ax_directchild_breaks
\newcommand{\axaxdirectchildbreaks}{
Commands on a parent and a child node break every filesystem
if the pair is not a construction pair
and the commands do not simply assert a directory at the parent
or an empty node at the child:
$\cxypnv\cc\czwnv \equiv \cbrk$ when $\cxypnv\cc\czwnv$ is not a construction pair, 
$\cxypnv\neq\cdda{\pn}$ and $\czwnv\neq\cbba{n}$.
}

% ax_directparent_breaks
\newcommand{\axaxdirectparentbreaks}{
Commands on a child and parent node break every filesystem
if the pair is not a destruction pair
and the commands do not simply assert an empty node at the child
or a directory at the parent:
$\cxynv\cc\czwpnv \equiv \cbrk$ when $\cxynv\cc\czwpnv$ is not a destruction pair,
$\cxynv\neq\cbba{n}$ and $\czwpnv\neq\cdda{\pn}$.
}

>>>>

% ax_directchild_breaks
\newcommand{\axaxdirectchildbreaks}{
\begin{sloppypar}
Commands on a parent and a child node break every filesystem
if the pair is not a construction pair
and the commands do not simply assert a directory at the parent
or an empty node at the child:
$\cxypnv\cc\czwnv \equiv \cbrk$ when $\cxypnv\cc\czwnv$ is not a construction pair, 
$\cxypnv\neq\cdda{\pn}$ and $\czwnv\neq\cbba{n}$.
\end{sloppypar}
}

% ax_directparent_breaks
\newcommand{\axaxdirectparentbreaks}{
\begin{sloppypar}
Commands on a child and parent node break every filesystem
if the pair is not a destruction pair
and the commands do not simply assert an empty node at the child
or a directory at the parent:
$\cxynv\cc\czwpnv \equiv \cbrk$ when $\cxynv\cc\czwpnv$ is not a destruction pair,
$\cxynv\neq\cbba{n}$ and $\czwpnv\neq\cdda{\pn}$.
\end{sloppypar}
}

### 2018-07-20 p2/axioms.tex
Final changes

\Cref{incomparable_is_independent} follows independently from
the following lemma,
which characterizes independent commands in a more detailed way.

>>>>

\Cref{incomparable_is_independent} follows from
the next \namecref{independent_details},
which characterizes independent commands in a more detailed way.

### 2018-07-20 p2/rec-intro.tex
Final changes

We work based on the assumption that to achieve this, we need
to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
As some commands may have been applied to both filesystems, our first approximation
is to apply the commands in $\bmanp$ to $\FS_A$ and those in $\ambnp$ to $\FS_B$.
This, however, will break both filesystems if there have been incompatible updates
in $A$ and $B$. 
Our aim is therefore to provide an algorithm that selects the commands 
$\reca \subset A\setminus B$
and $\recb \subset B\setminus A$ 
so that $\reca\aFS_B\neq\fsbroken$ and $\recb\aFS_A\neq\fsbroken$,
and show that these are maximal in the sense that
adding any further command to $\reca$ or $\recb$ will break the filesystems.

We will work based on update sequences $A$ and $B$ that are simple.
If the reconciliation algorithm is to work on arbitrary sequences,
\cref{can_simplify} can be used to convert those sequences to simple ones.

@@

\myskip
We aim prove that $\reca$ and $\recb$ can be applied to the replicas,
that is, without loss of generality,
\[ \reca\aFS_B\neq\fsbroken. \]
So that we can formalize statements needed to prove this,
we introduce the partial order $\worksmeqsign$ that describes under what conditions
sequences of commands work, that is, do not break a filesystem.

>>>>

We work based on the assumption that to achieve this, we need
to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
As some commands may have been applied to both filesystems, our first approximation
is to apply the commands in $\bmanp$ to $\FS_A$ and those in $\ambnp$ to $\FS_B$.
This, however, will break both filesystems if there have been incompatible updates
in $A$ and $B$. 
Our aim is therefore to provide an algorithm that selects the commands 
$\reca \subset A\setminus B$
and $\recb \subset B\setminus A$ 
so that $\reca\aFS_B\neq\fsbroken$ and $\recb\aFS_A\neq\fsbroken$,
and show that these are the longest sequences with this property.

We will work based on update sequences $A$ and $B$ that are simple.
If the reconciliation algorithm is to work on arbitrary sequences,
\cref{can_simplify} can be used to convert these sequences to simple ones.

@@

\myskip
We aim prove that $\reca$ and $\recb$ can be applied to the replicas,
that is, without loss of generality,
\[ \reca\aFS_B\neq\fsbroken. \]
So that we can formalize statements needed to prove this,
we introduce the partial order $\worksmeqsign$ that describes conditions under which
sequences of commands work, that is, do not break a filesystem.

### 2018-07-20 p2/upd-correct.tex
Final changes

On systems where filesystem updates are recorded,
an alternative update detection algorithm is to
omit step 1, and use \cref{can_simplify} to simplify the series of recorded updates
into a simple sequence containing the necessary updates.
In fact, we use such a hypothetical record in the proof of \cref{update_works}.

% There is a sequence between any two states: destroy one completely and construct the other one. (finite FS)

@@

\begin{proof}
First, we create a sequence of commands $S$ for which $S\aFS=\FS^*$.
First, create a topological sort of all nodes in $\setn$ that are
not empty in $\FS$ so that children come first,
that is, if $n'\descendant n$, then $n$ precedes $n'$.
For each node in the given order, add a destruction command to a sequence $S_0$
that deletes the value at $n$.
We know that the commands will never break the filesystem, as the types of nodes
with empty children can be freely changed, and that $S_0\aFS$ is empty at all nodes.
Next, order nodes in $\setn$ that re not empty in $\FS^*$ in the reverse order,
that is, if $n'\descendant n$, then $n'$ precedes $n$.
Add a construction command to a sequence $S_1$ for each node that changes an empty value
to $\FS^*(n)$.
We know that $S_1$ is defined on an empty filesystem for the same reason,
and clearly $(S_0\cc S_1)\aFS=\FS^*$.
By \cref{can_simplify} there exists a simple $S$ for which $S\eqnrw (S_0\cc S_1)$.

>>>>

On systems where filesystem updates are recorded,
an alternative update detection algorithm is to
omit step 1, and use \cref{can_simplify} to simplify the series of recorded updates
into a simple sequence containing the necessary updates.

@@

\begin{proof}
First, we create a sequence of commands $S$ for which $S\aFS=\FS^*$.
We create a topological sort of all nodes in $\setn$ that are
not empty in $\FS$ so that children come first,
that is, if $n'\descendant n$, then $n$ precedes $n'$.
For each node in the given order, we add a destruction command to a sequence $S_0$
that deletes the value at $n$.
We know that the commands will never break the filesystem, as the types of nodes
with empty children can be freely changed, and that $S_0\aFS$ is empty at all nodes.
Next, we order nodes in $\setn$ that are not empty in $\FS^*$ in the reverse order,
that is, if $n'\descendant n$, then $n'$ precedes $n$.
We add a construction command to a sequence $S_1$ for each node that changes an empty value
to $\FS^*(n)$.
We know that $S_1$ is defined on an empty filesystem for the same reason,
and clearly $(S_0\cc S_1)\aFS=\FS^*$.
By \cref{can_simplify} there exists a simple $S$ for which $S\eqnrw (S_0\cc S_1)$.
